Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-14 manuscript/manuscript.tex
Edited proposed keywords
Fixed axe (for single axe) and axis (for plural)

\begin{keywords}
up to six keywords from the list
\end{keywords}

@@

Due to the rotational symmetry along the $z$ axis, the integration in $\lambda'$ is straightforward:

@@

The equation \ref{eq:shell-pot} allows to easily obtain the exact gravity field generated by a spherical shell with a variable density in depth on any outside point located in the $z$ axis.
Due to the rotational symmetry along any axe that passes through the centre of the shell, the potential in equation \ref{eq:shell-pot} reassembles the gravity field on any outside point at distance $r$ from the its centre.

>>>>

\begin{keywords}
Satellite gravity??, Numerical modelling, Structure of the Earth, Gravity anomalies and Earth structure, Numerical approximations and analysis, spatial analysis??
\end{keywords}

@@

Due to the rotational symmetry along the $z$ axe, the integration in $\lambda'$ is straightforward:

@@

The equation \ref{eq:shell-pot} allows to easily obtain the exact gravity field generated by a spherical shell with a variable density in depth on any outside point located in the $z$ axe.
Due to the rotational symmetry along any axe that passes through the centre of the shell, the potential in equation \ref{eq:shell-pot} reassembles the gravity field on any outside point at distance $r$ from the its centre.
